---
title: "milestone_3"
author: "Evelyn Cai"
date: "2/21/2020"
output: html_document
---

## Milestone 3
The article I am replicating is Daniel Smith et. al's "Identifying voter preferences for politicians’ personal attributes: a conjoint experiment in Japan". It is about whether voters really do prefer candidates with certain characteristics (immutable or not, such as gender and experience), or whether these preferences are induced by other causes such as PR vs. first-pass-the-post systems or regional vs. national political party organizing. For example, voters may not inherently prefer male candidates over female candidates, but may be induced to choose male candidates because of a first-pass-the-post system, in which there is less coordination among national parties to ensure their party's candidates are diverse and representative enough. Smith et. al chose a conjoint experimental method, which has recently become very popular in political science, to randomize every characteristic of a fake candidate so that the treatment effect of each characteristic can be parsed out later statistically.
[Link to the article is here.](https://www.cambridge.org/core/journals/political-science-research-and-methods/article/identifying-voter-preferences-for-politicians-personal-attributes-a-conjoint-experiment-in-japan/95ADB2B43C5289ECFE6898B7FE776CFE)
[Link to the replication files are here.](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/KCIADO)

What I did with the data thus far:
Their code is all in base R. I rewrote their data pre-processing code and plot-creating code using tidyverse/dplyr stuff. We love tidyverse stuff. Below is the code. I created a series of eight mosaic tables, the first four of which examines gender, the latter four of which examines age. Next, I created a rudimentary AMCE plot which examines the average treatment effect of gender for candidates for the lower house. The mosaic plots are numerically correct and match the original charts. However, the AMCE plot's numbers are wildly different. My next steps are to figure out why they're different and how to fix it.

[Link to my public Github repo for final project milestones is here.](https://github.com/caievelyn/milestone)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load necessary libraries
library(tidyverse)
library(utils)
library(ggmosaic)
library(ggplot2)
library(cregg)

# Decompress the file (Commented out because already completed once)
# untar(tarfile = "ReplicationPackage (1).tar.gz")

# Read in .csv files as dataframes
DD_lo <- read_csv("actual-lower-2014-allcandidates.csv")
DD_up <- read_csv("actual-upper-2013-allcandidates.csv")
```

```{r pre_processing_data, include = FALSE}
### Recoding Variables

## System type indicators

# Create a new column called win_type_1 that encodes the results from the
#DD_lo$result column.

DD_lo <- DD_lo %>%
  mutate(win_type_1 = as.factor(case_when(result == 1 ~ "SMD",
                                result == 2 ~"Zombie",
                                result == 3 ~ "PR",
                                TRUE ~ NA_character_)),
         elec_type_1 = case_when(prcode == 0 ~ "SMD",
                                 kucode == 0 ~ "PR",
                                 TRUE ~ "Both"),
         elec_type_2 = as.factor(case_when(elec_type_1 == "SMD" | elec_type_1 == "Both" ~ "SMD/Dual",
                                 TRUE ~ elec_type_1)))


DD_up <- DD_up %>%
  mutate(win_type_1 = as.factor(districttype),
         elec_type_1 = win_type_1,
         win_type_2 = as.factor(case_when(win_type_1 == "SMD" | win_type_1 == "MMD" ~ "SNTV",
                                win_type_1 == "PR" ~ "PR",
                                TRUE ~ NA_character_)),
         elec_type_2 = win_type_2)

# Recode values

DDD <- list(DD_lo, DD_up)

for(i in 1:length(DDD))
  {DD <- DDD[[i]] %>%
    mutate(win = case_when(result > 0 ~ 1,
                           TRUE ~ 0),
           celeb = as.factor(case_when(celeb == 0 ~ "No",
                                       celeb == 1 ~ "Yes",
                                       TRUE ~ NA_character_)),
           busi_emp = as.factor(case_when(busi_emp == 0 ~ "No",
                                          busi_emp == 1 ~ "Yes",
                                          TRUE ~ NA_character_)),
           busi_exec = as.factor(case_when(busi_exec == 0 ~ "No",
                                           busi_exec == 1 ~ "Yes",
                                           TRUE ~ NA_character_)),
           bcrat = as.factor(case_when(bcrat == 0 ~ "No",
                                       bcrat == 1 ~ "Yes",
                                       TRUE ~ NA_character_)),
           localbcrat = as.factor(case_when(localbcrat == 0 ~ "No",
                                            localbcrat == 1 ~ "Yes",
                                            TRUE ~ NA_character_)),
           pref_assy = as.factor(case_when(pref_assy == 0 ~ "No",
                                           pref_assy == 1 ~ "Yes",
                                           TRUE ~ NA_character_)),
           sec = as.factor(case_when(sec == 0 ~ "No",
                                     sec == 1 ~ "Yes",
                                     TRUE ~ NA_character_)),
           experience_lab = as.character(experience_lab),
           experience_lab = factor(experience_lab, levels = c("Currently in office, 3+ terms", "Currently in office, 2 terms", "Currently in office, 1 term", "Formerly in office, 3+ terms", "Formerly in office, 2 terms", "Formerly in office, 1 term", "No experience")),
           age_lab = as.character(case_when(age < 40 ~ "Under 40",
                                         age >= 40 & age < 60 ~ "50 - 59",
                                         age >= 60 & age < 70 ~ "60 - 69",
                                         age >= 70 ~ "70 or over",
                                         TRUE ~ NA_character_)),
           age_lab = factor(age_lab, levels = c("70 or over", "60 - 69", "50 - 59", "Under 40")),
           educ_lab = as.factor(case_when(educ_lab == "Local public university" ~ "Other public university",
                                          TRUE ~ educ_lab)),
           party_en = factor(party_en, levels = c("LDP", "Komeito", "JCP", "DPJ")),
           home_lab = factor(home_lab, ordered = TRUE),
           dynastic_lab = as_factor(case_when(dynastic_lab == "Local-level elected politician" ~ "Loc. Pol.",
                                              dynastic_lab == "National-level elected politician" ~ "MP",
                                              dynastic_lab == "Cabinet minister" ~ "Cab. Min.",
                                              TRUE ~ "None")))
           DDD[[i]] <- DD
}

# Unlist

DD_lo <- DDD[[1]]
DD_up <- DDD[[2]]

# Reorder Levels

# lower house
DD_lo %>%
  mutate(party_en = factor(party_en, levels = c("Independent","Other","PFG","JIP","LDP","Komeito","DPJ","PLP","SDP","JCP")))

# upper house
DD_up %>%
  mutate(party_en = factor(party_en, levels = c("Independent","Other","JIP","LDP","Komeito","DPJ","PLP","SDP","JCP")))

## Filter for winners

DD_lo_win <- DD_lo %>%
  filter(win == 1)

DD_up_win <- DD_up %>%
  filter(win == 1)
```

``` {r mosaic plot, echo = FALSE}

# load("ReplicationPackage/output/actual.RData")

set.seed(2389)

## gender (Fig A.1.a)
DD_lo$by <- DD_lo$gender_lab
DD_up$by <- DD_up$gender_lab
DD_lo_win$by <- DD_lo_win$gender_lab
DD_up_win$by <- DD_up_win$gender_lab

DD_lo_mosaic <- DD_lo %>%
  select(elec_type_2, by) %>%
  group_by(elec_type_2, by) %>%
  count()

# Mosaic plots by gender
gender_DD_lo <- ggplot(DD_lo) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = by)) +
  theme_light() +
  labs(title = "HR Candidates") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

gender_DD_up <- ggplot(DD_up) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = by)) +
  theme_light()+
  labs(title = "HC Candidates") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

gender_DD_lo_win <- ggplot(DD_lo_win) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = by)) +
  theme_light() +
  labs(title = "HR Winners") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

gender_DD_up_win <- ggplot(DD_up_win) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = by)) +
  theme_light() +
  labs(title = "HC Winners") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

gender_DD_lo
gender_DD_up
gender_DD_lo_win
gender_DD_up_win


# Mosaic plots by age
age_DD_lo <- ggplot(DD_lo) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = age_lab)) +
  theme_light() +
  labs(title = "HR Candidates") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

age_DD_up <- ggplot(DD_up) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = age_lab)) +
  theme_light()+
  labs(title = "HC Candidates") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

age_DD_lo_win <- ggplot(DD_lo_win) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = age_lab)) +
  theme_light() +
  labs(title = "HR Winners") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

age_DD_up_win <- ggplot(DD_up_win) + 
  geom_mosaic(aes(x = product(elec_type_2), fill = age_lab)) +
  theme_light() +
  labs(title = "HC Winners") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25),
                     labels = c("0", "0.25", "0.50", "0.75", "1"))

# Call mosaic plots.
age_DD_lo
age_DD_up
age_DD_lo_win
age_DD_up_win

```

```{r AMCE_plots, echo= FALSE, warning = FALSE, error = FALSE}

# Create AMCE plots to determine the average treatment effect of gender. 

amces <- cj(DD_lo, win ~ age_lab + experience_lab + educ_lab + dynastic_lab + home_lab + party_en, estimate = "amce", 
            by = ~gender_lab)
diff_amces <- cj(DD_lo, win ~ age_lab + experience_lab + educ_lab + dynastic_lab + home_lab + party_en, estimate = "amce_diff", 
                 by = ~gender_lab)
plot(rbind(amces, diff_amces)) + ggplot2::facet_wrap(~BY, ncol = 3L)

```