---
title: "milestone_2"
author: "Evelyn Cai"
date: "2/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries

library(tidyverse)
library(utils)
```

## Milestone 2
The article I am now replicating is Daniel Smith's "Identifying voter preferences for politicians’ personal attributes: a conjoint experiment in Japan". It is about whether voters really do prefer male candidates over female candidates or vice versa inherently, or whether this is induced by other causes such as PR vs. first-pass-the-post systems or regional vs. national political party organizing. [Link to the article is here.](https://www.cambridge.org/core/journals/political-science-research-and-methods/article/identifying-voter-preferences-for-politicians-personal-attributes-a-conjoint-experiment-in-japan/95ADB2B43C5289ECFE6898B7FE776CFE)
[Link to the replication files are here.](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/KCIADO)
What I did with the data:
Smith's code is all in base R. He has a file that pre-processes and cleans the data by recoding variables. I rewrote this file using tidyverse stuff. We love tidyverse stuff. Below is the code. I call summary() on the code.

```{r pre_process, include = FALSE}

### Pre-Processing Data

# Load necessary libraries

library(tidyverse)
library(utils)

# Decompress the file

untar(tarfile = "ReplicationPackage (1).tar.gz")

# Read in .csv files as dataframes

DD_lo <- read_csv("actual-lower-2014-allcandidates.csv")
DD_up <- read_csv("actual-upper-2013-allcandidates.csv")

### Recoding Variables

## System type indicators

# Create a new column called win_type_1 that encodes the results from the
#DD_lo$result column.

DD_lo <- DD_lo %>%
  mutate(win_type_1 = as.factor(case_when(result == 1 ~ "SMD",
                                result == 2 ~"Zombie",
                                result == 3 ~ "PR",
                                TRUE ~ NA_character_)),
         elec_type_1 = case_when(prcode == 0 ~ "SMD",
                                 kucode == 0 ~ "PR",
                                 TRUE ~ "Both"),
         elec_type_2 = as.factor(case_when(elec_type_1 == "SMD" | elec_type_1 == "Both" ~ "SMD/Dual",
                                 TRUE ~ elec_type_1)))


DD_up <- DD_up %>%
  mutate(win_type_1 = as.factor(districttype),
         elec_type_1 = win_type_1,
         win_type_2 = as.factor(case_when(win_type_1 == "SMD" | win_type_1 == "MMD" ~ "SNTV",
                                win_type_1 == "PR" ~ "PR",
                                TRUE ~ NA_character_)),
         elec_type_2 = win_type_2)

# Recode values

DDD <- list(DD_lo, DD_up)

for(i in 1:length(DDD))
  {DD <- DDD[[i]] %>%
    mutate(win = case_when(result > 0 ~ 1,
                           TRUE ~ 0),
           celeb = as.factor(case_when(celeb == 0 ~ "No",
                                       celeb == 1 ~ "Yes",
                                       TRUE ~ NA_character_)),
           busi_emp = as.factor(case_when(busi_emp == 0 ~ "No",
                                          busi_emp == 1 ~ "Yes",
                                          TRUE ~ NA_character_)),
           busi_exec = as.factor(case_when(busi_exec == 0 ~ "No",
                                           busi_exec == 1 ~ "Yes",
                                           TRUE ~ NA_character_)),
           bcrat = as.factor(case_when(bcrat == 0 ~ "No",
                                       bcrat == 1 ~ "Yes",
                                       TRUE ~ NA_character_)),
           localbcrat = as.factor(case_when(localbcrat == 0 ~ "No",
                                            localbcrat == 1 ~ "Yes",
                                            TRUE ~ NA_character_)),
           pref_assy = as.factor(case_when(pref_assy == 0 ~ "No",
                                           pref_assy == 1 ~ "Yes",
                                           TRUE ~ NA_character_)),
           sec = as.factor(case_when(sec == 0 ~ "No",
                                     sec == 1 ~ "Yes",
                                     TRUE ~ NA_character_)),
           age_lab = as.factor(case_when(age < 40 ~ "Under 40",
                                         age >= 40 & age < 60 ~ "50 - 59",
                                         age >= 60 & age < 70 ~ "60 - 69",
                                         age >= 70 ~ "70 or over",
                                         TRUE ~ NA_character_)),
           educ_lab = as.factor(case_when(educ_lab == "Local public university" ~ "Other public university",
                                          TRUE ~ educ_lab)),
           dynastic_lab = as_factor(case_when(dynastic_lab == "Local-level elected politician" ~ "Loc. Pol.",
                                              dynastic_lab == "National-level elected politician" ~ "MP",
                                              dynastic_lab == "Cabinet minister" ~ "Cab. Min.")))
           DDD[[i]] <- DD
}

# Unlist

DD_lo <- DDD[[1]]
DD_up <- DDD[[2]]

# Reorder Levels

# lower house
DD_lo %>%
  mutate(party_en = factor(party_en, levels = c("Independent","Other","PFG","JIP","LDP","Komeito","DPJ","PLP","SDP","JCP")))

# upper house
DD_up %>%
  mutate(party_en = factor(party_en, levels = c("Independent","Other","JIP","LDP","Komeito","DPJ","PLP","SDP","JCP")))

## Filter for winners

DD_lo_win <- DD_lo %>%
  filter(win == 1)

DD_up_win <- DD_up %>%
  filter(win == 1)

# Need to do: 
 # Reorder factor levels for age_lab
# DD$age_lab <- factor(DD$age_lab, levels(DD$age_lab)[c(5,1,2,3,4)])

```

```{r summary, echo = FALSE}

# Show summary

summary(DD_lo)
summary(DD_up)

```



